---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# smexplorer  [![Travis-CI Build Status](https://travis-ci.org/BroVic/smexplorer.svg?branch=master)](https://travis-ci.org/BroVic/smexplorer)  
_An R package for the exploratory analysis of social media data_  

## Installation
This is accomplished by running these 2 lines in the R console. If you need to install R, get it [**here**](https://cloud.r-project.org):
```{r installation, eval=FALSE}
if (!requireNamespace(devtools)) install.packages("devtools")
devtools::install_github("BroVic/smexplorer")
```

Note the following:

* First-time installion of `smexplorer` on a **shiny, brand-new** R platform takes time, due to concomitant installation of several dependencies.
* If installation breaks off due to network problems, rerun `devtools::install_github("BroVic/smexplorer")`
* You need [Java Runtime Environment](http://www.java.com/download) (v. 1.8 or greater) to use `smexplorer`. Run `java -version` in the shell (e.g. *Command Prompt* for Windows, _Terminal_ for OS X) to check.

Upon installing `smexplorer`, further instructions for its use can be obtained with
```{r vignette, eval=FALSE}
vignette("smexplorer")
```

[**Email**](mailto:victor.ordu@nesrea.gov.ng)
